Mixing time estimation in reversible Markov chains from a single sample path

### 2015-06-02 abstract.tex
.

%!TEX root =  matrix-est.tex
This article provides an efficient procedure for estimating the mixing
time of a reversible ergodic Markov chain.
The procedure computes the estimate from a single finite-length sample
path from the Markov chain, and does not require any \emph{a priori}
bounds on the mixing time itself.
This stands in contrast to previous approaches, which either require a
reset mechanism or require additional prior knowledge.
Most notably, the procedure produces a fully empirical confidence
interval (i.e., it depends only on the sample path and a given
confidence parameter $\delta$) that is always valid with probability
$1-\delta$; and the width of the interval converges to zero at a
$\sqrt{n}$-rate, where $n$ is the length of the sample path.

>>>>

%!TEX root =  matrix-est.tex
This article provides an efficient procedure for estimating the mixing
time of a reversible ergodic Markov chain.
The procedure computes the estimate from a single finite-length sample
path from the Markov chain, and does not require any \emph{a priori}
bounds on the mixing time itself.
This stands in contrast to previous approaches, which either require a
reset mechanism or require additional prior knowledge.
Most notably, the procedure produces a fully empirical confidence
interval (i.e., it depends only on the sample path and a given
confidence parameter $\delta$) that is always valid with probability
$1-\delta$; and the width of the interval converges to zero at a
$\sqrt{n}$ rate, where $n$ is the length of the sample path.
